Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-12-11 paper/main.tex
adjust table for coming additional parameter values

\begin{table}[H]
    \centering
    \begin{tabular}{l c c c c c c}
        \multicolumn{4}{l}{\textbf{Growth Parameters for different Methods}}\\
        \toprule
        % \multicolumn{6}{Growth Rates}\\
        Method & Cell $0$ & Cell $1$ & Cell $2$ & Cell $3$ & Cell $4$ & Cell $5$\\
        \midrule
        Fit             & 0.00703 & 0.00540 & 0.01159 & 0.00756 & 0.01024 & 0.00836\\
        \ac{abm} Direct & 0.00671 & 0.00746 & 0.01138 & 0.00848 & 0.02005 & 0.00952\\
        \textbf{Imaging values will be adjusted!}\\
        \ac{abm} Imaging& 0.00104 & 0.00146 & 0.00206 & 0.00286 & 0.00190 & 0.00171\\
        & \textbf{Daughters}\\
        \midrule
        & Cell $0$ & Cell $1$ & Cell $2$ & Cell $3$ & Cell $4$ & Cell $5$\\
        & 0.00240 & 0.00494 & 0.00096 & 0.00363\\
        & 0.00490 & 0.00226 & 0.00448 & 0.00048\\
        % 0.0014057073 & 0.0010807540 & 0.0023177727 & 0.0015120675 & 0.0020488179 & 0.0016726263\\
        % direct & 0.0009785162 & 0.0012641432 & 0.0021701728 & 0.0015695889 & 0.0036255661 & 0.0018419186\\
        \bottomrule
    \end{tabular}
    \caption{
        \textbf{TODO maybe report uncertainties?;
        Update and explain these values. And also add units!;
        FIX NUMERICAL VALUES;
        check ordering of values}
    }
    \label{tab:comparison-growth-rates}
\end{table}

>>>>

\begin{table}[H]
    \centering
    \textbf{Growth Parameters obtained by various Methods}
    \begin{tabular}{l c c c c c c}
        % \multicolumn{7}{l}{}\\
        % \multicolumn{6}{Growth Rates}\\
        & Cell $0$ & Cell $1$ & Cell $2$ & Cell $3$ & Cell $4$ & Cell $5$\\
        \toprule
        Exponential Fit & 0.00703 & 0.00540 & 0.01159 & 0.00756 & 0.01024 & 0.00836\\
        % \multicolumn{7}{l}{\textbf{Direct Position-Space Metric}}\\
        \midrule
        Direct \ac{abm} Mie    & 0.00671 & 0.00746 & 0.01138 & 0.00848 & 0.02005 & 0.00952\\
        Direct \ac{abm} Morse  & \textbf{TODO}\\
        % \multicolumn{7}{l}{\textbf{Lineage-Aware Image-Space Metric (TODO)}}\\
        \midrule
        Imaging \ac{abm} Mie & 0.00104 & 0.00146 & 0.00206 & 0.00286 & 0.00190 & 0.00171\\
        % & \textbf{Daughters}\\
        % \midrule
        % & Cell $0$ & Cell $1$ & Cell $2$ & Cell $3$ & Cell $4$ & Cell $5$\\
        Daughter 0 & 0.00240 & 0.00494 & 0.00096 & 0.00363 & - & -\\
        Daughter 1 & 0.00490 & 0.00226 & 0.00448 & 0.00048 & - & -\\
        % 0.0014057073 & 0.0010807540 & 0.0023177727 & 0.0015120675 & 0.0020488179 & 0.0016726263\\
        % direct & 0.0009785162 & 0.0012641432 & 0.0021701728 & 0.0015695889 & 0.0036255661 & 0.0018419186\\
        \bottomrule
    \end{tabular}
    \caption{
        \textbf{TODO maybe report uncertainties?;
        Update and explain these values. And also add units!;
        FIX NUMERICAL VALUES;
        check ordering of values}
    }
    \label{tab:comparison-growth-rates}
\end{table}
